---
title: "Bringing it All Together"
description: "Bringing it all together for a short course at the Conference on Statistical Practice 2020"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, fig.pos = 'H', fig.align="center")
```


## Bringing It all together 

Here we try to bring it all together show how to use the template and some debugging practices. 

### Using the template

We should have everything together at this point. All we need to do now is build the package, and find the template in the RStudio IDE menu. To make changes to the template all you need to do is update the R package and reinstall. In the LaTeX document we had several variables that we can specify in the YAML hearder such as `documentclass`, `title`, `subtitle`, `toc`, `boxes`, `date`, `Team`, `Group`, and `authors`. This list isn't exhaustive, but we will hit the high points.

### Debuging Issues

Debugging templates can be difficult. Most of our problems are going to come from our template. The `keep_tex` option will be very useful when looking for problems. We can take the source tex, and look for specific errors in the LaTeX. We can also use the `boxes` options to look at the placement of logos, titles, and authors. 

## `ggplot2` themes

We review creating `ggplot2` themes, and at it's heart themes can be created with the `theme` function in `ggplot2`.

```{r}
theme_csp <- function(base_size = 11, base_family = "",
                          base_line_size = base_size / 22,
                          base_rect_size = base_size / 22) {
  theme_bw(
    base_size = base_size,
    base_family = base_family,
    base_line_size = base_line_size,
    base_rect_size = base_rect_size
  ) %+replace%
    theme(
      # no background and no grid
      panel.border     = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),

      # show axes
      axis.line      = element_line(colour = "black", size = rel(1)),

      # match legend key to panel.background
      legend.key       = element_blank(),

      # simple, black and white strips
      strip.background = element_rect(fill = "white", colour = "black", size = rel(2)),
      # NB: size is 1 but clipped, it looks like the 0.5 of the axes

      complete = TRUE
    )
}
```

```{r}
theme_grey <- function(base_size = 11, base_family = "",
                       base_line_size = base_size / 22,
                       base_rect_size = base_size / 22) {

  # The half-line (base-fontsize / 2) sets up the basic vertical
  # rhythm of the theme. Most margins will be set to this value.
  # However, when we work with relative sizes, we may want to multiply
  # `half_line` with the appropriate relative size. This applies in
  # particular for axis tick sizes. And also, for axis ticks and
  # axis titles, `half_size` is too large a distance, and we use `half_size/2`
  # instead.
  half_line <- base_size / 2

  # Throughout the theme, we use three font sizes, `base_size` (`rel(1)`)
  # for normal, `rel(0.8)` for small, and `rel(1.2)` for large.

  t <- theme(
    # Elements in this first block aren't used directly, but are inherited
    # by others
    line =               element_line(
                           colour = "black", size = base_line_size,
                           linetype = 1, lineend = "butt"
                         ),
    rect =               element_rect(
                           fill = "white", colour = "black",
                           size = base_rect_size, linetype = 1
                         ),
    text =               element_text(
                            family = base_family, face = "plain",
                            colour = "black", size = base_size,
                            lineheight = 0.9, hjust = 0.5, vjust = 0.5, angle = 0,
                            margin = margin(), debug = FALSE
                         ),

    axis.line =          element_blank(),
    axis.line.x =        NULL,
    axis.line.y =        NULL,
    axis.text =          element_text(size = rel(0.8), colour = "grey30"),
    axis.text.x =        element_text(margin = margin(t = 0.8 * half_line / 2), vjust = 1),
    axis.text.x.top =    element_text(margin = margin(b = 0.8 * half_line / 2), vjust = 0),
    axis.text.y =        element_text(margin = margin(r = 0.8 * half_line / 2), hjust = 1),
    axis.text.y.right =  element_text(margin = margin(l = 0.8 * half_line / 2), hjust = 0),
    axis.ticks =         element_line(colour = "grey20"),
    axis.ticks.length =  unit(half_line / 2, "pt"),
    axis.ticks.length.x = NULL,
    axis.ticks.length.x.top = NULL,
    axis.ticks.length.x.bottom = NULL,
    axis.ticks.length.y = NULL,
    axis.ticks.length.y.left = NULL,
    axis.ticks.length.y.right = NULL,
    axis.title.x =       element_text(
                           margin = margin(t = half_line / 2),
                           vjust = 1
                         ),
    axis.title.x.top =   element_text(
                           margin = margin(b = half_line / 2),
                           vjust = 0
                         ),
    axis.title.y =       element_text(
                           angle = 90,
                           margin = margin(r = half_line / 2),
                           vjust = 1
                         ),
    axis.title.y.right = element_text(
                           angle = -90,
                           margin = margin(l = half_line / 2),
                           vjust = 0
                         ),

    legend.background =  element_rect(colour = NA),
    legend.spacing =     unit(2 * half_line, "pt"),
    legend.spacing.x =    NULL,
    legend.spacing.y =    NULL,
    legend.margin =      margin(half_line, half_line, half_line, half_line),
    legend.key =         element_rect(fill = "grey95", colour = NA),
    legend.key.size =    unit(1.2, "lines"),
    legend.key.height =  NULL,
    legend.key.width =   NULL,
    legend.text =        element_text(size = rel(0.8)),
    legend.text.align =  NULL,
    legend.title =       element_text(hjust = 0),
    legend.title.align = NULL,
    legend.position =    "right",
    legend.direction =   NULL,
    legend.justification = "center",
    legend.box =         NULL,
    legend.box.margin =  margin(0, 0, 0, 0, "cm"),
    legend.box.background = element_blank(),
    legend.box.spacing = unit(2 * half_line, "pt"),

    panel.background =   element_rect(fill = "grey92", colour = NA),
    panel.border =       element_blank(),
    panel.grid =         element_line(colour = "white"),
    panel.grid.minor =   element_line(size = rel(0.5)),
    panel.spacing =      unit(half_line, "pt"),
    panel.spacing.x =    NULL,
    panel.spacing.y =    NULL,
    panel.ontop    =     FALSE,

    strip.background =   element_rect(fill = "grey85", colour = NA),
    strip.text =         element_text(
                           colour = "grey10",
                           size = rel(0.8),
                           margin = margin(0.8 * half_line, 0.8 * half_line, 0.8 * half_line, 0.8 * half_line)
                         ),
    strip.text.x =       NULL,
    strip.text.y =       element_text(angle = -90),
    strip.text.y.left =  element_text(angle = 90),
    strip.placement =    "inside",
    strip.placement.x =  NULL,
    strip.placement.y =  NULL,
    strip.switch.pad.grid = unit(half_line / 2, "pt"),
    strip.switch.pad.wrap = unit(half_line / 2, "pt"),

    plot.background =    element_rect(colour = "white"),
    plot.title =         element_text( # font size "large"
                           size = rel(1.2),
                           hjust = 0, vjust = 1,
                           margin = margin(b = half_line)
                         ),
    plot.title.position = "panel",
    plot.subtitle =      element_text( # font size "regular"
                           hjust = 0, vjust = 1,
                           margin = margin(b = half_line)
                         ),
    plot.caption =       element_text( # font size "small"
                           size = rel(0.8),
                           hjust = 1, vjust = 1,
                           margin = margin(t = half_line)
                         ),
    plot.caption.position = "panel",
    plot.tag =           element_text(
                           size = rel(1.2),
                           hjust = 0.5, vjust = 0.5
                         ),
    plot.tag.position =  'topleft',
    plot.margin =        margin(half_line, half_line, half_line, half_line),

    complete = TRUE
  )

  # make sure all elements are set to NULL if not explicitly defined
  ggplot_global$theme_all_null %+replace% t
}
```




